### 2025-06-17 simulation.qmd
20250617 - memory handling

```{r}
#| label: put-simulated-data-in-format-for-scoring

bootstappedStats$data_src <- bootstappedStats$iteration

bootstappedStatsByPosition <- split(
  bootstappedStats,
  by = "pos",
  keep.by = TRUE)

bootstappedStatsByPosition <- lapply(
  bootstappedStatsByPosition,
  as_tibble)

@@

@@

>>>>

```{r}
#| label: put-simulated-data-in-format-for-scoring1

data.table::setnames(bootstappedStats, "iteration", "data_src") # data.table equivalent to: bootstappedStats$data_src <- bootstappedStats$iteration

bootstappedStatsByPosition <- split(
  bootstappedStats,
  by = "pos",
  keep.by = TRUE)
```

@@

```{r}
#| label: put-simulated-data-in-format-for-scoring1

bootstappedStatsByPosition <- lapply(
  bootstappedStatsByPosition,
  setDF)

@@

```{r}
#| label: free-up-memory7
#| include: false
